Plots for Latent Hawkes Paper

### 2020-10-15 output_scripts/Paper_Plots.Rmd
add plot to compare ks plots from m1 and m2

slides_plots <- FALSE
```

@@

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
out <- captureOutput(for(current_cohort in fit_cohorts){
  naive_rank_10[[current_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[current_cohort]]])
  expert_rank_10[[current_cohort]] <- expertRankHierarchy(full_data[[cohort_names[current_cohort]]])
})

@@

```{r define_functions}
model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1+exp(-eta3*(x-y))))})

@@

```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE}
current_cohort <- 5

@@

col_obj <- list(x.vec = seq(0,max(as.vector(ks.stat.matrix)),length.out = 100),
                col.vec = viridis(100))

temp <- cLegend(as.vector(ks.stat.matrix))
#which(temp$x.vec == as.vector(ks.stat.matrix))
## need to adjust this for the legend also.
# image(1, cLegend(as.vector(ks.stat.matrix))$x.vec,
#       matrix(data=cLegend(as.vector(ks.stat.matrix))$x.vec, 
#              ncol=length(cLegend(as.vector(ks.stat.matrix))$x.vec),nrow=1),
#       col=cLegend(as.vector(ks.stat.matrix))$col.vec,
#       xlab="",ylab="",axes=FALSE)
image(1, col_obj$x.vec,
      matrix(data=col_obj$x.vec, 
             ncol=length(col_obj$x.vec),nrow=1),
      col=col_obj$col.vec,
      xlab="",ylab="",axes=FALSE)
axis(4, at=c(0,0.3,0.6), labels=c(0,0.3,0.6), las= HORIZONTAL<-1,
     cex.axis=2.4)

@@

```{r fig-3a-baseline-rate}
current_cohort <- 5

@@

```{r fig-3b-rank-comparison}
current_cohort <- 5

@@

```{r fig_3b_update, fig.height=7}
# 2 -> 11 might be good here
current_cohort <- 5
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

plot(ecdf(Lambda.dc_hawkes.test), do.points = FALSE,
     verticals = TRUE, col = viridis::viridis(1), lwd = 2, 
     xlab = "", ylab = "", xaxt = "n", yaxt = "n",
     main = "", col.01line = NULL)
curve(pexp(x,1/mean(Lambda.dc_hawkes.test)),
      min(Lambda.dc_hawkes.test), max(Lambda.dc_hawkes.test),
      ylab = "", xlab = "", axes = FALSE,
      add = TRUE, lwd = 2)

@@

```{r repeat entire fig2b for model 2}
current_cohort <- 5

@@

@@

@@

```{r fig-6a-rank-vs-isi}
### Rank Comparison for Single Cohort ####
current_cohort <- 5

@@

```{r fig-7-prMatrix-Cohort5, fig.height=7}
current_cohort <- 5

@@

```{r fig_pr_slides, fig.height=3, fig.width=7, include=slides_plots,eval=slides_plots}
current_cohort <- 5

@@

```{r fig-8a-frob-norm-cohort5}
load("../output/plot_N_predict.RData")
current_cohort <- 5# cohort 1 looks worse than rest

@@

```{r fig-pred-cohort-slides, include=slides_plots,eval=slides_plots, fig.height=3}
load("../output/plot_N_predict.RData")
current_cohort <- 5# cohort 1 looks worse than rest
# 3 looks nice

@@

```{r fig-9a-spearman-rank-cohort1}
load("../output/plot_rank_predict.RData")
current_cohort <- 5
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),width=600,height=300)
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #scale_fill_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank correlation") +
  ylim(0, 1)
p5
```

```{r fig-pred-cor, eval=slides_plots,include=slides_plots,fig.height=3}
load("../output/plot_rank_predict.RData")
current_cohort <- 5
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),width=600,height=300)
temp_plot_df <- temp_plot_df %>%
  filter(method != "I-MMHP") 
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #scale_fill_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
  #ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Rank correlation") +
  ylim(0, 1)
p5
```

@@

current_cohort <- 5

@@

```{r process for state separation cohort5,eval=FALSE}
# only run this once and save the results
# this doesn't need to be rerun ever, even if the stan fits change
current_cohort <- 5

@@

```{r process data for plot 10b}
library(PlayerRatings)
current_cohort <- 5
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_poisson_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_state_separation_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
sub.types <- c("All", "Active", "Inactive"); # three methods
task.types <- paste0("day", 1:21);

>>>>

slides_plots <- FALSE
current_cohort <- 5
```

@@

# Define the cohorts will be fitted
fit_cohorts <- c(1:10)
naive_rank_10 <- list()
expert_rank_10 <- list()
out <- captureOutput(for(curr_cohort in fit_cohorts){
  naive_rank_10[[curr_cohort]] <- naiveRankHierarchy(full_data[[cohort_names[curr_cohort]]])
  expert_rank_10[[curr_cohort]] <- expertRankHierarchy(full_data[[cohort_names[curr_cohort]]])
})

@@

```{r define_functions}
model1_fn <- list(alpha.fun = function(x,y,eta1,eta2,eta3){return(eta1*x*y*exp(-eta2*abs(x-y))/(1 +
                                                        exp(-eta3*(x-y))))})

@@

```{r fig-2b-diag-plot,echo=FALSE,warning=FALSE}
# current_cohort <- 5

@@

####
par(oma = c(6,4,4,1), mar=rep(0,4),
    mgp = c(0, .2, 0))
layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
                    byrow = TRUE),rep(12*12+1,12)), 
       widths=c(rep(1,12),2), heights=rep(1,12))
for(i in expert_rank_10[[current_cohort]]){
  for(j in expert_rank_10[[current_cohort]]){
    if(ks.stat.matrix[i,j]==0){
      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
           axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
           border = 0, col = 'white')
    }else{
      Lambda.test <- Lambda_matrix[i,j][[1]]
      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
            ylab="",xlab="",axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4], 
           border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
            ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
      plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE,
           verticals = TRUE, col = "red", lwd = 2)
    }
  }
}
par(mar = c(0,2,0,3),mgp=c(0,0.8,0))
m1_ks <- ks.stat.matrix
col_obj <- list(x.vec = seq(0,max(as.vector(ks.stat.matrix)),length.out = 100),
                col.vec = viridis(100))

temp <- cLegend(as.vector(ks.stat.matrix))
#which(temp$x.vec == as.vector(ks.stat.matrix))
## need to adjust this for the legend also.
# image(1, cLegend(as.vector(ks.stat.matrix))$x.vec,
#       matrix(data=cLegend(as.vector(ks.stat.matrix))$x.vec, 
#              ncol=length(cLegend(as.vector(ks.stat.matrix))$x.vec),nrow=1),
#       col=cLegend(as.vector(ks.stat.matrix))$col.vec,
#       xlab="",ylab="",axes=FALSE)
image(1, col_obj$x.vec,
      matrix(data=col_obj$x.vec, 
             ncol=length(col_obj$x.vec),nrow=1),
      col=col_obj$col.vec,
      xlab="",ylab="", axes = FALSE)
axis(4, at=c(0,0.3,0.6), labels=c(0,0.3,0.6), las= HORIZONTAL<-1,
     cex.axis=2.4)

@@

```{r fig-3a-baseline-rate}
# current_cohort <- 5

@@

```{r fig-3b-rank-comparison}
# current_cohort <- 5

@@

```{r fig_3b_update, fig.height=7}
# 2 -> 11 might be good here
# current_cohort <- 5
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
return_df <- cleanObservationPeriod(current_cohort, clean_data)
unique_pairs_df <- return_df %>% group_by(initiator, recipient) %>%
  dplyr::summarize(count=n(),
            observe=list(observe.id),
            observe.length=list(observe.time),
            no.events=list(no.events)) 
top_pairs <- unique_pairs_df %>% arrange(desc(count))

@@

plot(ecdf(Lambda.dc_hawkes.test), do.points = FALSE,
     verticals = TRUE, col = viridis::viridis(1), lwd = 2, 
     xlab = "", ylab = "", xaxt = "n", yaxt = "n",
     main = "", col.01line = NULL)
curve(pexp(x,1/mean(Lambda.dc_hawkes.test)),
      min(Lambda.dc_hawkes.test), max(Lambda.dc_hawkes.test),
      ylab = "", xlab = "",
      add = TRUE, lwd = 2)

@@

```{r repeat entire fig2b for model 2}
# current_cohort <- 5

@@

m2_ks <- ks.stat.matrix

@@

```{r}
ks_diff <-  (m2_ks - m1_ks)/m1_ks
ks_diff[is.nan(ks_diff)] <- 0
# -------------- KS plot (stat)
col.vec <- cRamp(as.vector(ks_diff))
## need to do some sort of transformation between these here
vir_cols <- viridis::viridis(length((as.vector(ks_diff))))
#order(as.vector(ks.stat.matrix),method = "")

values <- as.vector(ks_diff)
sorted_vals <- sort(ks_diff)
#match(values,sorted_vals)
col.vec.vir <- vir_cols[match(values,sorted_vals)]

####
par(oma = c(6,4,4,1), mar=rep(0,4),
    mgp = c(0, .2, 0))
layout(cbind(matrix(data=c(1:(12*12)), nrow = 12, ncol = 12, 
                    byrow = TRUE),rep(12*12+1,12)), 
       widths=c(rep(1,12),2), heights=rep(1,12))
for(i in expert_rank_10[[current_cohort]]){
  for(j in expert_rank_10[[current_cohort]]){
    if(ks_diff[i,j]==0){
      plot(0,0,xlim=c(0,5),ylim=c(0,5),type="n", xlab="", ylab="", 
           axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
           border = 0, col = 'white')
    }else{
      Lambda.test <- Lambda_matrix[i,j][[1]]
      curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
            ylab="",xlab="",axes = FALSE, frame=TRUE)
      rect(par('usr')[1],par('usr')[3],par('usr')[2],par('usr')[4],
           border = 0, col = col.vec.vir[matrixToVecIdx(i,j,mice_number)])
      # curve(pexp(x,1/mean(Lambda.test)), min(Lambda.test), max(Lambda.test),
      #       ylab="",xlab="",axes = FALSE, frame=TRUE,add=TRUE, lwd=2)
      # plot(ecdf(Lambda.test), add = TRUE, do.points = FALSE,
      #      verticals = TRUE, col = "red", lwd = 2)
    }
  }
}
par(mar = c(0,2,0,3),mgp=c(0,0.8,0))

col_obj <- list(x.vec = seq(min(as.vector(ks_diff)),max(as.vector(ks_diff)),
                            length.out = 100),
                col.vec = viridis(100))

# temp <- cLegend(as.vector(ks_diff))

image(1, col_obj$x.vec,
      matrix(data=col_obj$x.vec, 
             ncol=length(col_obj$x.vec),nrow=1),
      col=col_obj$col.vec,
      xlab="",ylab="")
# axis(4, at=c(-0.2,0,0.2), labels=c(-0.2,0,0.2), las= HORIZONTAL<-1,
#      cex.axis=2.4)

mtext(text=expert_rank_10[[current_cohort]], side=1,
      line=1.8, outer=TRUE, cex=1.8,
      at=1/14*c(1:12)-1/22)
mtext(text = expert_rank_10[[current_cohort]],
      side = 2, line = 0.5, outer = TRUE, cex = 1.8,
      at =1/12*c(12:1)-1/20, las = 2)
mtext(text = "(M2 - M1)/M1", side = 3, line = 1.4, outer = TRUE,
      cex = 2.2,
      at=0.45, font=2)

@@

```{r fig-6a-rank-vs-isi}
### Rank Comparison for Single Cohort ####
# current_cohort <- 5

@@

```{r fig-7-prMatrix-Cohort5, fig.height=7}
# current_cohort <- 5

@@

```{r fig_pr_slides, fig.height=3, fig.width=7, include=slides_plots,eval=slides_plots}
# current_cohort <- 5

@@

```{r fig-8a-frob-norm-cohort5}
load("../output/plot_N_predict.RData")
# current_cohort <- 5# cohort 1 looks worse than rest

@@

```{r fig-pred-cohort-slides, include=slides_plots,eval=slides_plots, fig.height=3}
load("../output/plot_N_predict.RData")
# current_cohort <- 5# cohort 1 looks worse than rest
# 3 looks nice

@@

```{r fig-9a-spearman-rank-cohort1}
load("../output/plot_rank_predict.RData")
# current_cohort <- 5
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),width=600,height=300)
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #scale_fill_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
  ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Spearman rank correlation") +
  ylim(0, 1)
p5
```

```{r fig-pred-cor, eval=slides_plots,include=slides_plots,fig.height=3}
load("../output/plot_rank_predict.RData")
# current_cohort <- 5
temp_plot_df <- predict_day_rank_df_lst[[current_cohort]]
temp_plot_df$method <- factor(temp_plot_df$method,
                              levels = c("mmhp","dsnl","m1","m2","m3"),
                              labels = c("I-MMHP","DSNL","C-HP","C-DCHP","C-MMHP"))
temp_plot_df$day <- factor(temp_plot_df$day)
# png(paste(plot_path,"real_predict_rank_one_cohort.png",sep=""),width=600,height=300)
temp_plot_df <- temp_plot_df %>%
  filter(method != "I-MMHP") 
p5 <- ggplot(temp_plot_df, aes(x = method, y = spearman, fill = method)) +
  geom_boxplot(alpha=0.7) +
  scale_fill_manual(values = viridis::viridis(5)) +
  #scale_fill_manual(values = c("gray","yellowgreen","steelblue","goldenrod2","firebrick2")) + 
  #ggtitle("(a)") +
  theme_bw() +
  theme(plot.title = element_text(size = 22, hjust = 0.5, face="bold"),
        text = element_text(size = 20),
        axis.text.x=element_blank(),
        axis.ticks.x = element_blank(), 
        legend.position="right") +
  facet_grid(cols=vars(day)) +
  xlab("Prediction horizon (day)") + 
  ylab("Rank correlation") +
  ylim(0, 1)
p5
```

@@

# current_cohort <- 5

@@

```{r process for state separation cohort5,eval=FALSE}
# only run this once and save the results
# this doesn't need to be rerun ever, even if the stan fits change
# current_cohort <- 5

@@

```{r process data for plot 10b}
library(PlayerRatings)
# current_cohort <- 5
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_poisson_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
load(paste(data_path,cohort_names[current_cohort],
           "/dsnl_state_separation_stan_result_",cohort_names[current_cohort],
           ".RData",sep=''))
sub.types <- c("All", "Active", "Inactive"); # three methods
task.types <- paste0("day", 1:21);
